\begin{thebibliography}{11}
	\bibitem{Tzu-Yi Yu:2014}
		Tzu-Yi Yu, Jiann-Cherng Yang, Yeong-Lin Lai, Chih-Cheng Chen and Han-Yu
		Chang.
		\newblock{\em Applying an Enhanced Heuristic Algorithm to a Constrained 
		Two-Dimensional Cutting Stock Problem.}
		\newblock{26 Mar. 2014.}\\
		\newblock{\url{http://www.naturalspublishing.com/files/published/7z5uf8oq7y668r.pdf}}
	
	\bibitem{Delgadillo:2007}
		Rosa Sumactika Delgadillo Avila.
		\newblock{\em Un estudio algorítmico del problema de corte y
		empaquetado 2D.}
		\newblock{Lima, Perú 2007.}\\
		\newblock{\url{http://cybertesis.unmsm.edu.pe/bitstream/cybertesis/1518/1/delgadillo_ar.pdf}}
		
	\bibitem{Karp:1972}
		Richard M. Karp.
		\newblock {\em Reducibility Among Combinatorial Problems}

	\bibitem{Gilmore:1961}
		P. Gilmore and R. Gomory.
		\newblock {\em A linear programming approach to the cutting stock 
		problem}.

	\bibitem{Gilmore:1963}
		P. Gilmore and R. Gomory.
		\newblock {\em A linear programming approach to the cutting stock 
		problem - Part II}.

	\bibitem{Gilmore:1965}
		P. Gilmore and R. Gomory.
		\newblock {\em Multistage Cutting Stock Problems of Two and More
		Dimensions}.

	\bibitem{Beasley:1985}
		J. E. Beasley.
		\newblock {\em Algorithms for unconstrained two-dimensional guillotine
		cutting}.
		\newblock Journal of the Operational Research Society, 1985.

	\bibitem{Chris:1977}
		N Christofides, C Whitlock.
		\newblock {\em An algorithm for two-dimensional cutting problems}.
		\newblock Operations Research, 1977.

	\bibitem{Viswa:1993}
		KV Viswanathan, A Bagchi.
		\newblock {\em Best-first search methods for constrained two-dimensional
		cutting stock problems}.
		\newblock Operations Research, 1993.

	\bibitem{Hifi:1997}
		M Hifi, R Ouafi.
		\newblock {\em Best-first search and dynamic programming methods for
		cutting problems: the cases of one or more stock plates}.
		\newblock Computers \& industrial engineering, 1997.

	\bibitem{Wang:1983}
		PY Wang
		\newblock {\em Two algorithms for constrained two-dimensional cutting
		stock problems}.
		\newblock Operations Research, 1983.

	\bibitem{Vasco:1989}
		FJ Vasko.
		\newblock {\em A computational improvement to Wang's two-dimensional
		cutting stock algorithm}.
		\newblock Computers \& industrial engineering, 1989.

	\bibitem{Olib:1990}
		J. F. Oliveira, J. S. Ferreira.
		\newblock {\em An improved version of Wang's algorithm for
		two-dimensional cutting problems}.
		\newblock European Journal of Operational Research, 1990.

	\bibitem{Valdes:2000}
		A. P. Guevara, J. M. T. Goerlich, R. A Valdés.
		\newblock {\em Algoritmos Grasp y Tabu Search para el problema de corte
		guillotina bidimendional}.
		\newblock XXV Congreso Nacional de Estadística e Investigación
		Operativa: Vigo, 2000.

	\bibitem{Golver:1997}
		F. Golver.
		\newblock {\em Tabu search and adaptive memory programming — advances,
		applications and challenges}.
		\newblock Interfaces in computer science and operations research, 1997.

	\bibitem{Feo:1989}
		T. A. Feo, M. G. C. Resende.
		\newblock {\em A probabilistic heuristic for computationally difficult
		set covering problems}.
		\newblock Operation Research Letters, 1989.

	\bibitem{Holland:1975}
		J. E. Holland.
		\newblock {\em Adaptation in natural and artificial systems: An 
		introductory analysis with applications to biology, control, and 
		artificial intelligence}.
		\newblock 1975.

	\bibitem{Kirk:1983}
		S. Kirkpatrick, C. D. Gelatt, M. P. Vecchi.
		\newblock {\em Optimization by simmulated annealing}.
		\newblock science, 1983.

	\bibitem{Cerny:1985}
		V. Černý.
		\newblock {\em Thermodynamical approach to the traveling
		salesman problem: An efficient simulation algorithm}.
		\newblock Journal of optimization theory and applications,
		1985.

	\bibitem{Lai:1997}
		K. K. Lai, J. W. M. Chan.
		\newblock {\em Developing a simulated annealing algorithm 
		for the cutting stock problem}.
		\newblock Computers \& industrial engineering, 1997.

	\bibitem{Faina:1999}
		L. Faina.
		\newblock {\em An application of simulated annealing to the 
		cutting stock problem}.
		\newblock European Journal of Operational Research, 1999.
		
	\bibitem{Parada:1996}
		V. Parada, M. Sepúlveda, M. Solar, A. Gómes.
		\newblock {\em Solution for the constrained guillotine cutting 
		problem by simulated annealing}.
		\newblock Computers \& Operations Research, 1998.

	\bibitem{Jackobs:1993}
		S. Jakobs.
		\newblock {\em On genetic algorithms for the packing of polygons}.
		\newblock European Journal of Operational Research, 1996. 
	
	\bibitem{Wu:2006}
		Wu Tai-Hsi, Wu Yi-Hua, Chang Chin-Ju.
		\newblock {\em Solving Two-Dimensional Packing Problems by 
		Using a Genetic Algorithm.}.
		\newblock Journal of Science and Engineering Technology, 2006.

	\bibitem{Gon:2007}
		JF Gonçalves.
		\newblock {\em A hybrid genetic algorithm-heuristic for a 
		two-dimensional orthogonal packing problem}.
		\newblock European Journal of Operational Research, 2007.
	
	\bibitem{Dyckhoff:1990}
		H. Dyckhoff.
		\newblock {\em A typology of cutting and packing problems}.
		\newblock European Journal of Operational Research, 1990.	
\end{thebibliography}
